Reproduction

### 2024-10-16 pages/reproduction.qmd
docs(results): add extra TODO statements to results pages
docs(reproductions): add hernandez and wood

@@

**@lim_staff_2020:** Uses **python (numpy and pandas)** to model the transmission of COVID-19 in a laboratory. It examines the proportion of staff infected in scenarios varying the: number of shifts per day; number of staff per shift; overall staff pool; shift patterns; secondary attack rate of the virus; introduction of protective measures (social distancing and personal protective equipment). <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

@@

**@anagnostou_facs-charm_2022:** This paper includes two models - we have focussed just on the dynamiC Hospital wARd Management (CHARM) model. CHARM uses **Python (simpy)** to model intensive care units (ICU) in the COVID-19 pandemic (as well as subsequent stays in a recovery bed). It includes three types of admission to the ICU (emergency, elective or COVID-19). COVID-19 patients are kept seperate, and if they run out of capacity due to a surge in COVID-19 admissions, additional capacity can be pooled from the elective and emergency capacity. <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

@@

**@hernandez_optimal_2015:** TBC <!-- TODO -->

**@wood_value_2021:** TBC <!-- TODO -->

@@

| Study | Scope | Success | Time |
| --- | --- | --- | --- |
| Shoaib and Ramamohan 2022 | 17 items:<br>• 1 table<br>• 9 figures<br>• 7 in-text results | 16 out of 17 (94%) | 28h 14m |
| Huang et al. 2019 | 8 items:<br>• 5 figures<br>• 3 in-text results | 3 out of 8 (37.5%) | 24h 10m |
| Lim et al. 2020 | 9 items:<br>• 5 tables<br>• 4 figures | 9 out of 9 (100%) | 12h 27m |
| Kim et al. 2021 | 10 items:<br>• 3 tables<br>• 6 figures<br>• 1 in-text result | 10 out of 10 (100%) | 14h 42m |
| Anagnostou et al. 2022 | 1 item:<br>• 1 figure | 1 out of 1 (100%) | 2h 11m |
| Johnson et al. 2021 | 5 items:<br>• 1 table<br>• 4 figures | TBC | TBC |
| Hernandez et al. 2015 | 8 items:<br>• 6 figures<br>• 2 tables | TBC | TBC |
| Wood et al. 2021 | 5 items:<br>• 4 figures<br>• 1 table | TBC | TBC |

@@

<!-- TODO: Add Johnson et al. 2021, Hernandez et al. 2015 and Wood et al. 2021 once conducted reproduction -->

@@

# Hernandez et al. 2015
# TODO: Add times once completed reproduction

# Wood et al. 2021
# TODO: Add times once completed reproduction

# Create list with the dataframes, labels and colours, to use for each plot
to_plot = [
    (df_sho, 'Shoaib and<br>Ramamohan<br>2022', '#ee6677'),
    (df_hua, 'Huang et<br>al. 2019', '#228833'),
    (df_lim, 'Lim et<br>al. 2020', '#4477aa'),
    (df_kim, 'Kim et<br>al. 2021', '#ccbb44'),
    (df_ana, 'Anagnostou<br>et al. 2022', '#66ccee')
    # (df_joh, 'Johnson et<br>al. 2021', '#aa3377'),
    # (df_her, 'Hernandez<br>et al. 2015', '#117733'),
    # (df_woo, 'Woord et al.<br>2021', '#882255')
]
```

>>>>

<!-- TODO: Once complete, carefully go over again and check everything is correct -->

@@

**@lim_staff_2020:** Uses **python (NumPy and pandas)** to model the transmission of COVID-19 in a laboratory. It examines the proportion of staff infected in scenarios varying the: number of shifts per day; number of staff per shift; overall staff pool; shift patterns; secondary attack rate of the virus; introduction of protective measures (social distancing and personal protective equipment). <a href="https://pythonhealthdatascience.github.io/stars-reproduce-lim-2020/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

@@

**@anagnostou_facs-charm_2022:** This paper includes two models - we have focussed just on the dynamiC Hospital wARd Management (CHARM) model. CHARM uses **python (SimPy)** to model intensive care units (ICU) in the COVID-19 pandemic (as well as subsequent stays in a recovery bed). It includes three types of admission to the ICU (emergency, elective or COVID-19). COVID-19 patients are kept seperate, and if they run out of capacity due to a surge in COVID-19 admissions, additional capacity can be pooled from the elective and emergency capacity. <a href="https://pythonhealthdatascience.github.io/stars-reproduce-anagnostou-2022/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

@@

**@hernandez_optimal_2015:** This study models Points-of-Dispensing (PODs) in New York City. These are sites set up during a public health emergency to dispense counter-measures. The authors use evolutionary algorithms combined with discrete-event simulation to explore optimal staff numbers with regards to resource use, wait time and throughput. They use **python** for most of the analysis (with **SimPy** for the simulation component), but **R** to produce the plots and tables for the paper. <a href="https://pythonhealthdatascience.github.io/stars-reproduce-hernandez-2015/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

**@wood_value_2021:** This study uses discrete-event simulation (**R (base R, dplyr, tidyr)**) to explore the deaths and life years lost under different triage strategies for an intensive care unit, relative to a baseline strategy. The unit is modelled with 20 beds (varied from 10 to 200 in sensitivity analyses). Three different triage strategies are explored, under three different projected demand trajectories. <a href="https://pythonhealthdatascience.github.io/stars-reproduce-wood-2021/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

@@

| Study | Scope | Success | Time |
| --- | --- | --- | --- |
| Shoaib and Ramamohan 2022 | 17 items:<br>• 1 table<br>• 9 figures<br>• 7 in-text results | 16 out of 17 (94%) | 28h 14m |
| Huang et al. 2019 | 8 items:<br>• 5 figures<br>• 3 in-text results | 3 out of 8 (37.5%) | 24h 10m |
| Lim et al. 2020 | 9 items:<br>• 5 tables<br>• 4 figures | 9 out of 9 (100%) | 12h 27m |
| Kim et al. 2021 | 10 items:<br>• 3 tables<br>• 6 figures<br>• 1 in-text result | 10 out of 10 (100%) | 14h 42m |
| Anagnostou et al. 2022 | 1 item:<br>• 1 figure | 1 out of 1 (100%) | 2h 11m |
| Johnson et al. 2021 | 5 items:<br>• 1 table<br>• 4 figures | <!--TODO--> | <!--TODO--> |
| Hernandez et al. 2015 | 8 items:<br>• 6 figures<br>• 2 tables | 1 out of 8 (12.5%) | 17h 56m |
| Wood et al. 2021 | 5 items:<br>• 4 figures<br>• 1 table | 5 out of 5 (100%) | 3h 50m |

@@

<!-- TODO: Add Johnson et al. 2021 once conducted reproduction -->

@@

# Hernandez et al. 2015 (1/8)
time_her = [
    [1076, 'Figure 5'], # Finished work, not completed, adjust to set to NaN
    [696, 'Figure 6'],
    [np.nan, 'Figure 7'],
    [np.nan, 'Figure 8'],
    [np.nan, 'Figure 9'],
    [np.nan, 'Figure 10'],
    [np.nan, 'Table 3'],
    [np.nan, 'Table 4']]
df_her = process_times(time_her, adjust='Figure 5')

# Wood et al. 2021
time_woo = [
    [170, 'Figure 4'],
    [170, 'Table 4'],
    [170, 'Figure 5'],
    [170, 'Figure 6'],
    [230, 'Figure 7']]
df_woo = process_times(time_woo)

# Create list with the dataframes, labels and colours, to use for each plot
to_plot = [
    (df_sho, 'Shoaib and<br>Ramamohan<br>2022', '#ee6677'),
    (df_hua, 'Huang et<br>al. 2019', '#228833'),
    (df_lim, 'Lim et<br>al. 2020', '#4477aa'),
    (df_kim, 'Kim et<br>al. 2021', '#ccbb44'),
    (df_ana, 'Anagnostou<br>et al. 2022', '#66ccee'),
    # (df_joh, 'Johnson et<br>al. 2021', '#aa3377'),
    (df_her, 'Hernandez<br>et al. 2015', '#882255'),
    (df_woo, 'Wood et al.<br>2021', '#117733')
]
```
